---
title: "FluxnetEO usage"
author: "Koen Hufkens"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FluxnetEO usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(FluxnetEO)
library(ggplot2)
library(dplyr)
```

## Demo data

The package includes data from the `CG-Tch` site for testing and tutorial purposes, as well an internal site list derived from the FluxnetEO publication (including small corrections as presented).

The internal site list can be called using:

```{r}
library(FluxnetEO)
head(fluxnet_sites)
```

Larger demo data is stored in the package data directory (see below).

## Reading FluxnetEO netcdf summary data

The main functionality of this small package is to provide an easy routine to access FluxnetEO data in R for further synthesis. The below code shows you how to read in the cutout data from a given path. Note that this routine executed on a directory containing for example the MODIS data will summarize this data in one big tidy data frame (~3 GB in memory, 600 MB as compressed RDS file).

```{r}
# list all cutout summary files
files <- list.files(
  system.file(package = "FluxnetEO", "extdata"),
  utils::glob2rx("*_cutout.nc"),
  full.names = TRUE,
  recursive = TRUE
)

# loop over all files and bind
# them in one data frame
data <- lapply(files, function(file){
  feo_read_nc(
    file = file
  )
})

data <- do.call("rbind", data)

# print the data
print(head(data))
```

### Plot data


```{r }
# convert date string to date object
# for nice plotting
data <- data %>%
  mutate(
    date = as.Date(date)
  )

# quick ggplot graph of the MODIS Aqua daytime
# land surface temperature (LST)
ggplot(data) +
  geom_point(
    aes(
      date,
      LST_AQUA_Day
    )
  ) +
  theme_classic()
```


