---
title: "FluxnetEO usage"
author: "Koen Hufkens"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FluxnetEO usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(FluxnetEO)
```

## Demo data

The package includes data from the `CG-Tch` site for testing and tutorial purposes, as well an internal site list derived from the FluxnetEO publication (including small corrections as presented).

The internal site list can be called using:

```{r}
library(FluxnetEO)
head(fluxnet_sites)
```

Larger demo data is stored in the package data directory (see below).

## Reading FluxnetEO netcdf summary data

The main functionality of this small package is to provide an easy routine to access FluxnetEO data in R for further synthesis.


```{r}
# list all cutout summary files
files <- list.files(
  system.file(package = "FluxnetEO", "extdata"),
  utils::glob2rx("*_cutout.nc"),
  full.names = TRUE,
  recursive = TRUE
)

data <- lapply(files, function(file){
  feo_read_nc(
    file = file
  )
})

data <- do.call("rbind", data)

print(head(data))
```
